---
title: "Immigration Policy Graphic"
author: "Simone Chu"
date: "4/5/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(sf)
library(fs)
library(forcats)
library(ggplot2)
library(ggthemes)
library(gganimate)
library(gt)
library(grDevices)
library(tidyverse)
```

### A brief explanation of the project

I plan to compare ethnic diversity of various countries with their immigration policy, because I'm curious to see whether or not ethnic diversity impacts how open a country is to immigration. This graphic deals with one part of the data -- ethnic diversity based on linguistic diversity, courtesy of Ethnologue. 

Later on, I plan to overlay maps with ethnic diversity and the ability to see how open these countries' immigration policies are. But for now: 

```{r, getting_data, include=FALSE, warning=FALSE, cache=TRUE}

qog <- read_csv("qog_std_cs_jan18copy.csv",
                col_types = cols(
                   .default = col_character(),
                   turnout_scale = col_double(),
                   turnout_score = col_double(),
                   w_LV = col_double(),
                   w_RV = col_double(),
                   final_weight = col_double(),
                   timestamp = col_datetime(format = ""))) %>%
  select(cname, fe_cultdiv, wdi_migration, unna_gdppc) %>%
  filter(cname %in% c("Austria", "Australia", "Belgium", "Canada",
                        "Switzerland", "Chile", "Czech Republic",
                        "Germany", "Denmark", "Estonia", "Spain",
                        "Finland", "France (1963-)", "United Kingdom", "Greece",
                        "Hungary", "Ireland", "Israel", "Iceland",
                        "Italy", "Japan", "Korea, South", "Mexico",
                        "Luxembourg", "Netherlands", "Norway", "New Zealand",
                        "Poland", "Portugal", "Sweden", "Slovakia",
                        "Turkey", "United States")) %>%

    # I filtered for the 33 countries that have data in the IMPIC dataset. It took a little bit
    # of trial and error, because the names of countries were denoted differently in this dataset
    # than in the IMPIC dataset, but I eventually found the ones I wanted. 

    # However, because the Qualities of Governent dataset doesn't have information on ethnic
    # diversity in Iceland and Luxembourg, I'll be excluding those countries from my analysis 
    # of immigration policy later on. 
  
  mutate(cname = fct_recode(cname, "France" = "France (1963-)", "South Korea" = "Korea, South")) %>%

    # I don't like the irregularity in the country names, so I recoded the relevant factors. 

  mutate(wdi_migration = as.numeric(wdi_migration),
         unna_gdppc = as.numeric(unna_gdppc),
         fe_cultdiv = as.numeric(fe_cultdiv))

    # When I first tried to plot this, the graph looked weird -- and that's when I realized all the columns were characters instead of numbers. Wild. 

policy_data <- read_csv("impic2016.csv") %>%
  select(cntry, year, AvgS_ImmPol) %>%
  mutate(cntry = fct_recode(cntry, "Austria" = "at", "Australia" = "au", "Belgium" = "be",
                            "Canada" = "ca", "Switzerland" = "ch", "Chile" = "cl",
                            "Czech Republic" = "cz", "Germany" = "de", "Denmark" = "dk",
                            "EU Directives" = "eu", "Estonia" = "ee", "EU Regulation" = "er",
                            "Spain" = "es", "Finland" = "fi", "France" = "fr", 
                            "United Kingdom" = "gb", "Greece" = "gr", "Hungary" = "hu",
                            "Ireland" = "ie", "Israel" = "il", "Iceland" = "is",
                            "Italy" = "it", "Japan" = "jp", "South Korea" = "kr",
                            "Luxembourg" = "lu", "Mexico" = "mx", "Netherlands" = "nl",
                            "Norway" = "no", "New Zealand" = "nz", "Poland" = "pl",
                            "Portugal" = "pt", "Sweden" = "se", "Slovakia" = "sk",
                            "Turkey" = "tr", "United States" = "us"))

    # Recoded the country names so that I can more easily identify which data goes for each
    # country. 

cia <- read_csv("cia_ethnicgroups.csv")

    # I then joined the data from the CIA factbook with the QoG dataset. 

diversity <- inner_join(qog, cia, by = "cname")

    # And then joined all the datasets together. 

all_data <- inner_join(diversity, policy_data, by = c("cname" = "cntry"))

    # I filtered out the countries that I was not able to find



# Notes to self: make table of CIA diversity data
# figure out a way to make scatter plot better
# run regressions (sample by year?) 
```

```{r hist}
all_data %>%
  select(cname, AvgS_ImmPol, year, largest_group) %>%
  filter(year == 2008) %>%
  filter(!is.na(largest_group)) %>%
  arrange(cname) %>% 
  select(-cname, -year, -largest_group)

# ggplot(cia, aes(x = largest_group)) + 
#   geom_histogram(breaks = seq(0,1, by = 0.01))

```



```{r}

for_table <- cia %>%
  select(cname, largest_group) %>%
  filter(!is.na(largest_group)) %>%
  gt() %>%
    tab_header(title = "Size of Dominant Ethnic Groups",
             subtitle = "Percentages reflect how much of the population the dominant ethnic group represents.") %>%
    cols_label(cname = "Country", largest_group = "Size of Dominant Ethnic Group") %>%
    fmt_percent(columns = vars(largest_group),
                 decimals = 1) %>%
  tab_source_note(md("*Data from the CIA World Factbook.*"))

for_table

```



```{r gdp_vs_immigration, echo=FALSE, message=FALSE}
test <- all_data %>%
  filter(year == 2010)

ggplot(test, aes(x = largest_group, y = AvgS_ImmPol)) + 
  geom_point() +
  scale_y_continuous() +
  xlab("% of Country Composed of Majority Ethnic Group") + 
  ylab("Summary Immigration Policy Score") + 
  labs(title = "Ethnic Composition vs. Summary Immigration Policy Score")
  # theme(axis.text.x = element_text(angle = 90, hjust = 1))

fit = lm(AvgS_ImmPol ~ largest_group, test)
summary(fit)
plot(fit)

```
```{r change_over_time, message=FALSE, warning=FALSE}
mig_change <- read_csv("migration_and_change.csv") %>%
  select(-X6, -X7, -X8) %>%
  mutate(change = year_after - year_before)

mig_change %>%
  ggplot(aes(x = migration, y = change)) + 
  geom_point()

fit = lm(change ~ migration, mig_change)
summary(fit)
plot(fit)

```



```{r map_files, echo=FALSE, warning=FALSE}
# Getting map of the whole world, downloaded from  
#http://thematicmapping.org/downloads/world_borders.php : 

# unzip("TM_WORLD_BORDERS_SIMPL-0.3.zip") 
# 
# world_map <- read_sf("TM_WORLD_BORDERS_SIMPL-0.3.shp")

# https://gadm.org/data.html 

# ggplot(world_map) + 
#   geom_sf() + 
#   theme_light()  
```

